---
title: "Exploratory Data Analysis"
author: "Louise Braithwaite"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir=normalizePath('~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate'))
```

## Introduction

Exploratory data analysis was conducted on the processed data frames listed below: 

1. cases (the data pulled from the government API. The api requests were compiled into one data frame and the data was cleaned)
2. deaths (the data pulled from the government API. The api requests were compiled into one data frame and the data was cleaned)
3. mediantrafficLONG (Shiny data)
4. Commutingtraffic (anpr traffic count data (TotalTrafficLongjoin) filtered to include only the 12 commuting locations)
5. CommutingtrafficDay (Shiny data)
6. carparkLONG (the carpark data frame is pivoted to long format and a daily occupancy hours variable is created)
7. carparkSummary (Shiny data)
8. ped.daily.totals (Shiny data)
9. NorthumberlandSt.east (Shiny data)
10. NorthumberlandSt.west (Shiny data)
11. ped.summary (data frame of summary statistics for all locations) 
12. ped.flow (data frame of summary statistics filtered to include just Northumberland St near Fenwicks location)  


```{r 1. load dataframes, include = FALSE}
load(file = "~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate/cache/cases.RData")
load(file = "~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate/cache/deaths.RData")
load(file = "~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate/cache/mediantrafficLONG.RData")
load(file = "~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate/cache/Commutingtraffic.RData")
load(file = "~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate/cache/CommutingtrafficDay.RData")
load(file = "~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate/cache/carparkLONG.RData")
load(file = "~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate/cache/carparkSummary.RData")
load(file = "~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate/cache/ped.daily.totals.RData")
load(file = "~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate/cache/NorthumberlandSt.east.RData")
load(file = "~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate/cache/NorthumberlandSt.west.RData")
load(file = "~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate/cache/ped.summary.RData")
load(file = "~/Covid-19_Data_Wall/Covid-19_DataWall_ProjectTemplate/cache/ped.flow.RData")
```

### Cases


You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
